Security of deployed Android devices

### 2013-11-12 msg2013-11-13.tex
Changes to msg presentation after discussion with Alastair

 \pgfdeclareimage[height=0.7cm]{university-logo}{university-logo}
 \logo{\pgfuseimage{university-logo}}

@@

\begin{frame}{Device Analyser collects lots of Data}{}
 \begin{itemize}
  \note{}
  \item Android app by Daniel Wagner installed on user devices collecting data with consent.
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item ??? records, ??? years, ??? devices
  \item \url{http://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=50px]{dalogo}{figures/dalogo100}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

\begin{frame}{Device Analyzer collects different kinds of data}{}
% Specific research aim (3+ year time scale)
 \pgfdeclareimage[height=0.38\textheight]{da_main}{figures/da_screenshot_main_screen}
 \pgfdeclareimage[height=0.38\textheight]{da_app_data}{figures/da_screenshot_app_data}
 \pgfdeclareimage[height=0.38\textheight]{da_phone_usage}{figures/da_screenshot_phone_usage}
 \begin{center}
  \pgfuseimage{da_main} \hspace{1em} \pgfuseimage{da_app_data} \hspace{1em} \pgfuseimage{da_phone_usage}
 \end{center}
 \vspace{-1.5em}
 \begin{itemize}
  \item DA also collects information on the OS version information and build number.
  \note{}
 \end{itemize}

\end{frame}

\begin{frame}{Root equivalent vulnerabilities are interesting}{}
 \begin{itemize}
  \item Root exploits break out of the sandbox.
  \note{}
  \item They allow applications to do arbitrarily bad things
  \item They are used in ??-??\% of malware
  \item How many devices are vulnerable to these exploits?
 \end{itemize}
\end{frame}

\begin{frame}{Root equivalent vulnerabilities on Android}{}
\small \url{https://wiki.dtg.cl.cam.ac.uk/drt24/dasecurityupdates}\\
All Android vulnerabilities:
 \begin{itemize}
  \item exploid
  \item RageAgainstTheCage zygote
  \item RageAgainstTheCage adb setuid exhaustion
  \item KillingInTheNameOf psneuter ashmem
  \item zergRush
  \item levitator
  \item Gingerbreak
  \item APK signature verification - duplicate file entries
  \item APK signature verification - unsigned shorts
 \end{itemize}

\end{frame}

% Leverage of colleagues
\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.5\textwidth]{da_norm_api}{figures/da_norm_api}
 \pgfdeclareimage[width=0.5\textwidth]{play_norm_api}{figures/play_norm_api}
 \begin{center}
  \pgfuseimage{da_norm_api}
  \pgfuseimage{play_norm_api}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}

>>>>

 %\pgfdeclareimage[height=0.7cm]{university-logo}{university-logo}
 %\logo{\pgfuseimage{university-logo}}

@@

\begin{frame}{Device Analyser collects lots of data}{}
 \begin{itemize}
  \note{}
  \item Android app installed on user devices
  \item Collects data with consent and sends it to our server
  \item Built by Daniel Wagner
  \note{\\}
  \item Deployed since May 2011
  \note{\\}
  \item 70 billion records, 2000 years, 16000 devices %TODO update these numbers
  \item \url{http://deviceanalyzer.cl.cam.ac.uk/}
 \end{itemize}
 \pgfdeclareimage[height=90px]{dalogo}{figures/dalogo512}
 \begin{center}
  \pgfuseimage{dalogo}
 \end{center}
\end{frame}

\begin{frame}{Device Analyzer collects different kinds of data}{}
% Specific research aim (3+ year time scale)
 \pgfdeclareimage[height=0.75\textheight]{da_main}{figures/da_screenshot_main_screen}
 \pgfdeclareimage[height=0.75\textheight]{da_app_data}{figures/da_screenshot_app_data}
 \pgfdeclareimage[height=0.75\textheight]{da_phone_usage}{figures/da_screenshot_phone_usage}
 \begin{center}
  \vspace{-1em}
  \pgfuseimage{da_main} \pgfuseimage{da_app_data} \pgfuseimage{da_phone_usage}
 \end{center}
 \vspace{-1.5em}
 \begin{itemize}
  \item DA also collects information on the OS version information and build number.
  \note{}
 \end{itemize}
\end{frame}

\begin{frame}{Other data}{}
\begin{itemize}
 \item \Large{ \emph{OS Version}}
 \item \emph{Build number}
 \item Device name
 \item GPU version
 \item Phone features
 \item baseband version
 \item What else?
\end{itemize}
\end{frame}

\begin{frame}{Root equivalent vulnerabilities are interesting}{}
 \begin{itemize}
  \item Root exploits break out of the sandbox.
  \note{}
  \item They allow applications to do arbitrarily bad things
  \item They are used in 37\% of malware %TODO check this figure
  \item How many devices are vulnerable to these exploits?
 \end{itemize}
\end{frame}

\begin{frame}{Root equivalent vulnerabilities on Android}{}
\small \url{https://wiki.dtg.cl.cam.ac.uk/drt24/dasecurityupdates}\\
Vulnerabilities affecting all of Android (not manufacturer specific):
 \begin{itemize}
  \item exploid
  \item RageAgainstTheCage zygote
  \item RageAgainstTheCage adb setuid exhaustion
  \item KillingInTheNameOf psneuter ashmem
  \item zergRush
  \item levitator
  \item Gingerbreak
  \item APK signature verification - duplicate file entries
  \item APK signature verification - unsigned shorts
 \end{itemize}
There are also lots of manufacture/device specific vulnerabilities.
\end{frame}

 \pgfdeclareimage[height=0.9\textheight]{da_norm_api}{figures/da_norm_api}
 \pgfdeclareimage[height=0.9\textheight]{play_norm_api}{figures/play_norm_api}
\begin{frame}{Old versions of Android still in use -- Google Play API}{}
 \begin{center}
  \pgfuseimage{play_norm_api}
 \end{center}
\end{frame}

\begin{frame}{Old versions of Android still in use -- Device Analyzer}{}
 \begin{center}
  \pgfuseimage{da_norm_api}
 \end{center}
\end{frame}

\begin{frame}{Old versions of Android still in use}{Coarse grained API information}
 \pgfdeclareimage[width=0.5\textwidth]{da_norm_api_small}{figures/da_norm_api}
 \pgfdeclareimage[width=0.5\textwidth]{play_norm_api_small}{figures/play_norm_api}
 \begin{center}
  \pgfuseimage{da_norm_api_small}
  \pgfuseimage{play_norm_api_small}
 \end{center}
Device Analyzer data is representative of the versions of Android actually in use
\end{frame}
